Variants on the Flight and Maintenance Planning problem

### 2018-05-02 latex/notes/FMP_variants.tex
Add new bibliographie and notes on models. And CLAIO summary.

\usepackage{graphicx}
\usepackage{amssymb}

@@

@@

    \begin{align}
        & \text{Min}\; \sum_{i \in \mathcal{P}} x_i
    \end{align}

    \begin{align}
        & \sum_{i \in \mathcal{P}} A_{it}x_{i} \geq d_j & t \in \mathcal{T} \\
        & x_{i} \geq 0,\; integer \\
    \end{align}

@@

    \begin{align}
        & \text{Min}\; \sum_{i \in \mathcal{P}} x_i
    \end{align}

    \begin{align}
        & \sum_{i \in \mathcal{P}} A_{it}x_{i} \geq 1 & t \in \mathcal{T} \\
        & x_{i} \geq 0,\; binary \\
    \end{align}

@@

    Here, A needs to be created taking into account:
    1. The range of start of maintenances.
    2. The fixed duration of maintenances.
    3. The minimal distance between maintenances.

@@

    \begin{align}
        & \sum_{i \in \mathcal{P}} A_{it}x_{i} \leq M & t \in \mathcal{T} \\
        & x_{i} \geq 0,\; integer \\
    \end{align}

@@

    As modelled in Rieck2012.

@@

    \begin{itemize}
     \item fixed maintenance duration.
     \item min distance between maintenances that.
     \item each maintenance uses an amount of resource.
     \item objective: minimize the max number of maintenances.
    \end{itemize}

@@

    \noindent{
    \begin{tabular}{ll}
        $i \in \mathcal{V} = [\![1, n]\!]$ & Set of maintenance operations.\\
        $(i, j) \in \mathcal{A} = [\![1, v]\!]$ & Set of consecutive (i, j) maintenance operations.\\
        $i = 0$ & Artificial starting node.\\
        $i = n+1$ & Artificial ending node.\\
    \end{tabular}
    }

@@

    \begin{tabular}{ll}
        $p_{i}$ & Duration of maintenance $k$ of resource $i$.\\
        ${\delta}_{ij}$ & Minimum duration between two maintenances $i$ and $j$.\\
        $\mathbf{d}$ & Last period on the horizon.\\
        $r_{i}$ & Resources taken by maintenance $i$.\\
        % $\mathbf{{To}}_{i,k}$ & Minimum starting period for maintenance $k$ of resource $i$.\\
        % $\mathbf{{Ta}}_{i,k}$ & Maximum starting period for maintenance $k$ of resource $i$.\\
    \end{tabular}

@@

    \begin{itemize}
     \item $S_i$: the start of maintenance operation $i$.
    \end{itemize}

@@

    $f(S)$ needs to be defined still. But includes a way to smooth the use of resoures by the activities.

    \begin{align}
        f(S)
    \end{align}

    \begin{align}
        & S_j - S_i \geq \delta_{ij} & (i, j) \in \mathcal{A} \\
        & S_0 = 0 & \\
        & S_{n+1} = \mathbf{d}  \\
        & S_{i} \geq 0, i \in \mathcal{V} \\
    \end{align}

>>>>

\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{chngcntr}

\counterwithin*{equation}{section}
\counterwithin*{equation}{subsection}

@@

    As presented in \cite{Brunner2013}.

@@

    \begin{align}
        & \text{Min}\; \sum_{i \in \mathcal{P}} x_i \label{numPatterns}
    \end{align}

    \begin{align}
        & \sum_{i \in \mathcal{P}} A_{it}x_{i} \geq d_j & t \in \mathcal{T} \label{demand} \\
        & x_{i} \geq 0,\; integer \\
    \end{align}

    (\ref{numPatterns}) minimizes the number of workers. (\ref{demand}) defines the need to have at least a given number of workers at any given time.

@@

    \begin{align}
        & \text{Min}\; \sum_{i \in \mathcal{P}} x_i \label{numPatterns}
    \end{align}

    \begin{align}
        & \sum_{i \in \mathcal{P}} A_{it}x_{i} \geq 1 & t \in \mathcal{T} \label{demand} \\
        & x_{i} \geq 0,\; binary \\
    \end{align}

    (\ref{numPatterns}) minimizes the number of workers. (\ref{demand}) defines the need to have at least one worker working at any given time.

@@

    Here, A needs to be created taking into account:

    \begin{enumerate}
        \item The range of start of maintenances.
        \item The fixed duration of maintenances.
        \item The minimal distance between maintenances.
    \end{enumerate}

@@

    \begin{align}
        & \sum_{i \in \mathcal{P}} A_{it}x_{i} \leq M & t \in \mathcal{T} \label{numMaint} \\
        & x_{i} \geq 0,\; integer \\
    \end{align}

        (\ref{numMaint}) defines the $M$ variable as the maximum number of maintenances at any period of time.

@@

    As modelled in \cite{Rieck2012} and \cite{Neumann2000}.

@@

    \begin{itemize}
     \item fixed maintenance duration.
     \item min and max durations between maintenances that belong to the same aircraft.
     \item each maintenance uses an amount of resource. In this case 1.
     \item objective: minimize the max number of maintenances.
     \item There are two artificial activities representing the start and end of the horizon.
    \end{itemize}

@@

    \noindent{
    \begin{tabular}{ll}
        $i \in \mathcal{V} = [\![1, n]\!]$ & Set of maintenance operations.\\
        $(i, j) \in \mathcal{E} = [\![1, v]\!]$ & Set of consecutive (i, j) maintenance operations, i.e. consecutive maintenances belonging to the same aircraft.\\
        $k \in \mathcal{R}$ & Types of resources that maintenance can take. We only have one type.\\
        $i = 0$ & Artificial starting node.\\
        $i = n+1$ & Artificial ending node.\\
    \end{tabular}
    }

@@

    \begin{tabular}{ll}
        $p_i$ & Duration of maintenance $i$.\\
        $\mathbf{d}$ & Last period on the horizon.\\
        $r_{ik}$ & Resources of type $k$ taken by maintenance $i$. In this case it's always 1 per maintenance.\\
        $d^{max}_{ij}$ & Maximum duration between two maintenances $i$ and $j$.\\
        $d^{min}_{ij}$ & Minimum duration between two maintenances $i$ and $j$.\\
        ${\delta}_{ij}$ & Precedence duration arcs between two maintenances $i$ and $j$ based on $d^{max}$ and $d^{min}$.\\
        $R_k$ & total maintenance capacity at each period for resource $k$.\\
        $c_k$ & cost per unit of investment on resource $k$.
        % $\mathbf{{To}}_{i,k}$ & Minimum starting period for maintenance $k$ of resource $i$.\\
        % $\mathbf{{Ta}}_{i,k}$ & Maximum starting period for maintenance $k$ of resource $i$.\\
    \end{tabular}

@@

    \begin{tabular}{ll}
        $S_i$ & the start of maintenance operation $i$.\\
        $\mathcal{A}(S^{\mathcal{C}}, t)$ & set of maintenance operations active at moment $t$.\\
    \end{tabular}

@@

    The following formulation is taken from \cite{Neumann2000}.

    \begin{align}
        \min f(\mathbf{R}(S)) = \sum_{k \in \mathcal{R}} c_k \max_{t \in \mathcal{T}} r_k(S^{\mathcal{C}}, t)
    \end{align}

    \begin{align}
        & S_j - S_i \geq \delta_{ij} & (i, j) \in \mathcal{E}  \label{precedence}\\
        & S_0 = 0 &  \label{firstjob}\\
        & S_{n+1} \leq \mathbf{d}   \label{lastjob}\\
        & S_{i} \in \mathbb{Z}_{\geq 0} & i \in \mathcal{V}  \label{integervars}\\
        & r_k(S^{\mathcal{C}}, t) = \sum_{i \in \mathcal{A}(S^{\mathcal{C}}, t)} r_{ik}  \label{consumptiondef}\\
        & r_k(S^{\mathcal{C}}, t) \leq R_k \label{consumptionmax}\\
    \end{align}

    (\ref{precedence}) constraints define the relative minimum and maximum starting times of tasks.
    (\ref{firstjob}) and (\ref{lastjob}) constraints define the fictitious start and end jobs.
    (\ref{integervars}) define the range for the starting time variables: integer positive.
    (\ref{consumptiondef}) defines the used quantity for each type of resource depending on the starting times and durations and (\ref{consumptionmax}) defines the maximum amount of resources of each type that can be used at any given time.

% As it has been shown by Bartusch et al. (1988),
% the feasible region S (without the integrality
% constraints S i 2 Z, i 2 V ) of R   is generally dis-
% connected and represents the union of (convex)
% polytopes whose number grows exponentially in n.
% The decision problem whether or not S 6 ;

% \bibliographystyle{dcu}
\bibliographystyle{alpha}
\bibliography{./../biblio/Scheduling,./../biblio/NRP}
